---
title: "Codebook"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE)
```
Codebook
========

Variables in tidy.txt
------------------------------

The variables are a subset of the original varibles described in the features_info.txt of the original data set
http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones

The test and training sets have been concatenated into a overal data table. (The 561-feature vector with time and frequency domain variables together with avtivity label and subject)  
From this overall data table **only the features with a mean or standard deviation (std) have been subsetted**  
From the subsetted overall data set, the tidy data set is summarizing the variables for all activities and subjects creating an average.  
Find the description of the code leading to the subsetted dataset in `run_analysis.md`.  


Variable name    | Description
-----------------|--------------------------------------------------------------------------------
label_activity   | Activity name
subject          | ID the subject (person) performing the activity with the smartphone recording the data. Its range is from 1 to 30.
...              | (see below)



See the original features description.
A extract of this is given here: 

### Feature Selection 

The features selected for this database come from the accelerometer and gyroscope 3-axial raw signals tAcc-XYZ and tGyro-XYZ. These time domain signals (prefix 't' to denote time) were captured at a constant rate of 50 Hz. The acceleration signal was then separated into body and gravity acceleration signals (tBodyAcc-XYZ and tGravityAcc-XYZ). 

The body linear acceleration and angular velocity were derived in time to obtain Jerk signals (tBodyAccJerk-XYZ and tBodyGyroJerk-XYZ).

Fast Fourier Transform (FFT) was applied to some of these signals producing fBodyAcc-XYZ,  fBodyAccJerk-XYZ,  fBodyGyro-XYZ 
(Note the 'f' to indicate frequency domain signals). 

These signals were used to estimate variables of the feature vector for each pattern:  
'-XYZ' is used to denote 3-axial signals in the X, Y and Z directions.

The complete list of variables of each feature vector is available in 'features.txt' of the original dataset


Dataset structure 
-----------------
(when converted to data.table)

```{r echo=FALSE}
load("./mydata.Rdata")
str(tidydata)
```

